Road traffic sound level estimation from realistic urban sound mixtures by Non-negative Matrix Factorization

### 2018-04-09 paper/articleNmfTrafficSimScene2018.tex
aknowledgment + funding add

The perceptual test is conducted with a panel of 50 subjects that are asked to assess the level of realism on a 7-point scale (1 is \textit{not realistic at all}, 7 is \textit{very realistic}) of a set of replicated and recorded scenes. The total number of sound scenes tested is set at 40. This is less than the number of scenes available to ensure that each audio sample is sufficiently assess. The first half includes 20 30-seconds audio files corresponding to the real scenes, including 5 scenes that belong to the sound environment \textit{park}, 6 from \textit{quiet street}, 4 from \textit{noisy street} and 5 from \textit{very noisy street} chosen randomly among the recorded scenes. The second half is composed of the replicated scenes from the evaluation corpus corresponding to the same 20 reference scenes. In order to limit the duration of the test to preserve the concentration of the subjects, each subject listens to only a subset of 20 sound scenes. All the scenes are normalized to the same sound level, chosen at 65 dB, and the subjects are not allowed to change the output sound level once set at the beginning of the experiment.

The experimental design is elaborated following a partially Balanced Incomplete Block Design (PBIBD) \cite{john1977optimal} the audio allocated to each participant and the listening order. This process allows to each sound sample to be assess almost the same number of time and to avoid statistical biais. The experimental design and the listening order per participant are performed with the package \textit{sensoMineR} on the \textit{R} software \cite{le_sensominer:_2008}.\\

@@

For reproducibility purposes, the evaluation corpus, the experimental protocol and the programs developed under the Matlab software are available online \footnote{\url{https://github.com/jean-remyGloaguen/articleNmfTrafficSimScene2018}} as the sound dataset \footnote{\url{https://zenodo.org/record/1184443#.WqfVb3wiGpo}}.

>>>>

The perceptual test is conducted with a panel of 50 listeners that are asked to assess the level of realism on a 7-point scale (1 is \textit{not realistic at all}, 7 is \textit{very realistic}) of a set of replicated and recorded scenes. The total number of sound scenes tested is set at 40. This is less than the number of scenes available to ensure that each audio sample is sufficiently assess. The first half includes 20 30-seconds audio files corresponding to the real scenes, including 5 scenes that belong to the sound environment \textit{park}, 6 from \textit{quiet street}, 4 from \textit{noisy street} and 5 from \textit{very noisy street} chosen randomly among the recorded scenes. The second half is composed of the replicated scenes from the evaluation corpus corresponding to the same 20 reference scenes. In order to limit the duration of the test to preserve the concentration of the subjects, each subject listens to only a subset of 20 sound scenes. All the scenes are normalized to the same sound level, chosen at 65 dB, and the subjects are not allowed to change the output sound level once set at the beginning of the experiment.

The experimental design is elaborated following a partially Balanced Incomplete Block Design (PBIBD) \cite{john1977optimal} the audio allocated to each participant and the listening order. This process allows to each sound sample to be assessed almost the same number of time and to avoid statistical biais. The experimental design and the listening order per participant are performed with the package \textit{sensoMineR} on the \textit{R} software \cite{le_sensominer:_2008}.\\

@@

For reproducibility purposes, the evaluation corpus, the experimental protocol and the programs developed under the Matlab software are available online \footnote{\url{https://github.com/jean-remyGloaguen/articleNmfTrafficSimScene2018}} as the sound dataset \footnote{\url{https://zenodo.org/record/1184443}}.

\section*{Acknowledgements}
The authors would like to thank Pierre Aumond and Catherine Lavandier from the University of Cergy-Pontoise for transmitting us the data of the \textit{Grafic} project.

\section*{Funding}
This study is co-funded by Ifsttar and Pays de la Loire region.
% with a partial funding from the ANR under project reference ANR-16-CE22-0012.
